\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

To numerically compute \eqref{KineticProx}, we employ the probability-weighted scattered point cloud-based proximal algorithm proposed in \cite{caluya2019TAC}.

@@

\begin{figure}
\centering
\includegraphics[width=.8\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed algorithmic setup for propagating the joint state PDF as probability weighted scattered point cloud $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$. The location of the points $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ can be updated by Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\varrho_{k}^{i}\}_{i=1}^{N}$ can be updated via discrete version of the proximal recursion (\ref{ProxRecursionInfiniteDim}).}}
\label{fig:BlockDiagm}
\end{figure}

>>>>

To numerically compute \eqref{KineticProx}, we employ the proximal algorithm proposed in \cite{caluya2019TAC} with finite $N$ samples. Specifically, the proximal algorithm recursively updates probability-weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$.

@@

\begin{figure}
\centering
\includegraphics[width=.8\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed algorithmic setup for propagating the joint state PDF as probability weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$. The location of the points $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ can be updated by Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ can be updated via discrete version of the proximal recursion (\ref{ProxRecursionInfiniteDim}).}}
\label{fig:BlockDiagm}
\end{figure}
